mixModelE1data

### 2018-08-16 E2/analysis/mixModelE2data.Rmd
starting analysis

#tidy data
library(dplyr)
df<- data
#to work with dplyr, can't have array field like letterSeq
df$letterSeq<- NULL

numItemsInStream<- length( data$letterSeq[1,] )  
minSPE<- -17; maxSPE<- 17

@@

Why are there NaNs for targetSP?
```{r}
table(is.nan(df$targetSP))

@@

@@

```{r}
dg<- df %>% filter(subject < "AC")

@@

Try to analyze one bit of data.
WHY ARE THERE NANS IN TARGETSP?
```{r}
library(mixRSVP)
dg<-df %>% filter(subject=="AA")
analyzeOneCondition(dg,numItemsInStream,parameterBounds(),nReplicates=5)

analyzeOneConditionDF(df %>% filter(subject=="AA"),numItemsInStream,parameterBounds(),nReplicates=5)

@@

Fit mixture model with R (if fitting not previously done and cached). 
```{r, echo=FALSE}

@@

condtnVariableNames <- c("subject","stream", "orientation")

>>>>

#tidy data
library(dplyr)
#to work with dplyr, can't have array field like letterSeq, so before I fixed it in turnMatIntoMeltedDataframe, 
#I dropped the letterSeq thusly:
#df$letterSeq<- NULL

numItemsInStream<- length( data[1,"letterSeq"]$letterSeq$`1` )  
minSPE<- -17; maxSPE<- 17

@@

Hm, seems like funky StackOverflow way of turning matrix elements into list gave it this weird name "1" with backticks around it

data[1,"letterSeq"]$letterSeq$`1`

Make condition names more sensible - stream (Left/Right) and orientation (Canonical/Inverted)
```{r}
E2<- data
names(E2)[names(E2) == 'target'] <-'stream'
names(E2)[names(E2) == 'condition'] <-'orientation'
E2$stream[ E2$stream==1 ] <- "Left"
E2$stream[ E2$stream==2 ] <- "Right"
E2$targetSide[ E2$targetSide==0 ] <- "Both"
E2$targetSide[ E2$targetSide==1 ] <- "Left"
E2$targetSide[ E2$targetSide==2 ] <- "Right"

#mutate condition to Orientation
E2$orientation[ E2$orientation==1 ] <- "Canonical"
E2$orientation[ E2$orientation==2 ] <- "Inverted"

@@

NaNs for targetSP indicate one-target trials, which are also indicated by targetSide==0
```{r}

table(E2$targetSP, E2$targetSide, dnn=c("targetSP","targetSide"), useNA="ifany")

```
Proportion of one-target trials seems to be `r table(is.nan(df$targetSP))["TRUE"] / sum( table(is.nan(df$targetSP)) )
`

@@

```{r}
dg<- E2 %>% filter(subject < "AC")

@@

Try to analyze one bit of data.
```{r}
library(mixRSVP)
dg<-E2 %>% filter(subject=="AA")
dg<-dg %>% filter( !is.nan(targetSP) )

analyzeOneCondition(dg,numItemsInStream,parameterBounds(),nReplicates=2)

analyzeOneConditionDF(dg,numItemsInStream,parameterBounds(),nReplicates=2)

@@

Maybe do the one-target trials first, might be faster.
```{r, echo=FALSE}
one<- dg %>% filter(targetSide != "Both")

condtnVariableNames <- c("subject","targetSide", "stream", "orientation")  
#It seems there are no rows for one-target (targetSide!="Both") and stream!=targetSide,
# which would mean that I can't test for stream swaps in the one-target condition

estimates<- dg  %>%  #  filter(subject=="AA") %>%
    group_by_(.dots = condtnVariableNames) %>%  #.dots needed when you have a variable containing multiple factor names
    do(  analyzeOneConditionDF(.,numItemsInStream,parameterBounds(),nReplicates=5) )

Fit mixture model (if fitting not previously done and cached). 
```{r, echo=FALSE}

@@
